sex

### 2021-08-26 data analysis/sex_analysis.Rmd
as

```{r}
library(emoGG)
library(tidyverse)
library(lubridate)
library(tidymodels)
library(yardstick)
library(broom)       # for making model summary tidy
library(visreg)      # for potting logodds and probability 
library(margins)     # to calculate Average Marginal Effects
library(rcompanion)  # to calculate pseudo R2
library(ROCR) 
#https://towardsdatascience.com/modelling-binary-logistic-regression-using-tidymodels-library-in-r-part-1-c1bdce0ac055
#https://towardsdatascience.com/modelling-binary-logistic-regression-using-r-research-oriented-modelling-and-interpretation-f67b3a954101
```

@@

>>>>

```{r}
library(emoGG)
library(tidyverse)
library(lubridate)
library(tidymodels)
library(ggtext)
library(yardstick)
library(broom)       # for making model summary tidy
library(visreg)      # for potting logodds and probability 
library(margins)     # to calculate Average Marginal Effects
library(rcompanion)  # to calculate pseudo R2
library(ROCR) 
#https://towardsdatascience.com/modelling-binary-logistic-regression-using-tidymodels-library-in-r-part-1-c1bdce0ac055
#https://towardsdatascience.com/modelling-binary-logistic-regression-using-r-research-oriented-modelling-and-interpretation-f67b3a954101
```

@@

```{r}
# predict the preproc_test dataset
preproc_test <- na.omit(preproc_test)
pred <- predict(model_logi, preproc_test, type="response") 
predicted <- round(pred) # round of the value; >0.5 will convert to 
                         # 1 else 0
# Creating a contigency table
tab <- table(Predicted = predicted, Reference = preproc_test$fem)
tab
```

```{r}
#preproc_test <- na.omit(preproc_test)
pred.rocr <- prediction(pred, preproc_test$fem)
eval <- performance(pred.rocr, "acc")
plot(eval)
```

```{r}
# Identifying the best cutoff value that maximizes accuracy
max <- which.max(slot(eval, "y.values")[[1]])
acc <- slot(eval, "y.values")[[1]][max] #y.values are accuracy 
                                        #measures
cut <- slot(eval, "x.values")[[1]][max] #x.values are cutoff 
                                        #measures
print(c(Accuracy = acc, Cutoff = cut))
```

```{r}
library(yardstick)
# Creating a actual/observed vs predicted dataframe
act_pred <- data.frame(observed = preproc_test$fem, predicted =  
                       factor(predicted))
# Calculating precision, recall and F1_score
prec <- precision(act_pred, observed, predicted)
rec <- recall(act_pred, observed, predicted)
F1_score <- f_meas(act_pred, observed, predicted) #called f_measure
print(prec)
print(rec)
print(F1_score)
```

```{r}
perf_rocr <- performance(pred.rocr, measure = "auc",
                         x.measure = "cutoff")
perf_rocr@y.values[[1]] <- round(perf_rocr@y.values[[1]], digits = 
                                 4)
perf.tpr.fpr.rocr <- performance(pred.rocr, "tpr", "fpr")
plot(perf.tpr.fpr.rocr, colorize=T, 
     main = paste("AUC:", (perf_rocr@y.values)))
abline(a = 0, b = 1)
```
